---
title: "NBA_Scraping"
output: word_document
date: "2025-06-04"
---

```{r setup, include=FALSE}

rm(list=ls(all=T)) #removing objects (how to clear environment)
knitr::opts_chunk$set(echo = TRUE)

library(hoopR)
library(dplyr)
library(ggplot2)
library(ggimage)
```

# Step 1: Scrape 3PT Shooting Stats from NBA API
## Data Cleaning for regular Season
```{r}
# Get full 2025 Playoff logs for ALL players
logs <- nba_playergamelogs(
  season = "2024-25",
  season_type = "Playoffs",
  league_id = "00",  # NBA (not G-League etc.)
  player_id = NULL   # <- THIS is what ensures it's not limited to just LeBron
)

# Extract actual log data
player_games <- logs$PlayerGameLogs
# Check number of rows (should be 100s)
nrow(player_games)
player_games_df <- as.data.frame(player_games)

library(ggplot2)
library(ggimage)


player_3pt_summary_playoffs <- player_games %>%
  select(PLAYER_NAME, PLAYER_ID, TEAM_ABBREVIATION, GAME_DATE,
         FG3M, FG3A, FG3_PCT, BLK, STL, PLUS_MINUS, REB, TOV, AST) %>%
  mutate(
    FG3M = as.numeric(FG3M),
    FG3A = as.numeric(FG3A),
    FG3_PCT = as.numeric(FG3_PCT),
    BLK = as.numeric(BLK),
    STL = as.numeric(STL),
    REB = as.numeric(REB),
    TOV = as.numeric(TOV),
    AST = as.numeric(AST),
    PLUS_MINUS = as.numeric(PLUS_MINUS)
  ) %>%
  group_by(PLAYER_NAME, PLAYER_ID) %>%
  summarise(
    TOTAL_FG3M = sum(FG3M, na.rm = TRUE),
    TOTAL_STLS = sum(STL, na.rm = TRUE),
    TOTAL_FG3A = sum(FG3A, na.rm = TRUE),
    AVG_FG3_PCT = mean(FG3_PCT, na.rm = TRUE),
    AVG_FG3_PCT2 = ifelse(TOTAL_FG3A == 0, 0, TOTAL_FG3M / TOTAL_FG3A),
    BPG = mean(BLK, na.rm = TRUE),
    SPG = mean(STL, na.rm = TRUE),
    RPG = mean(REB, na.rm = TRUE),
    TPG = mean(TOV, na.rm = TRUE),
    APG = mean(AST, na.rm = TRUE),
    STOCKS = sum(BPG, SPG, na.rm = TRUE),
    TOTAL_PLUS_MINUS = sum(PLUS_MINUS, na.rm = TRUE),
    GP = n(),
    .groups = "drop"
  ) %>% 
 filter(TOTAL_FG3A >= 1)

# Step 4: View result
#head(player_3pt_summary_playoffs)

player_3pt_summary_playoffs <- player_3pt_summary_playoffs %>%
  mutate(IMG_URL = paste0("https://cdn.nba.com/headshots/nba/latest/1040x760/", PLAYER_ID, ".png"))

#player_3pt_summary$IMG_URL <- paste0("https://cdn.nba.com/headshots/nba/latest/1040x760/", player_3pt_summary$PLAYER_ID, ".png")

league_avg_3p <- mean(player_3pt_summary_playoffs$AVG_FG3_PCT2, na.rm = TRUE) 

player_3pt_summary_playoffs <- player_3pt_summary_playoffs %>%
  mutate(
    SHOT_QUALITY = AVG_FG3_PCT*100,
    SHOT_QUALITY_2 = AVG_FG3_PCT2*100,
    SHOT_MAKING = AVG_FG3_PCT2*100 - league_avg_3p*100
  )

league_avg_3p_PO <- player_3pt_summary_playoffs %>%
  filter(TOTAL_FG3A >= 1) %>%
  summarise(
    league_avg = sum(TOTAL_FG3M, na.rm = TRUE) / sum(TOTAL_FG3A, na.rm = TRUE)
  ) 
league_avg_3p_value <- pull(league_avg_3p_PO, league_avg)

```

# 2025 NBA Playoffs: 3PT% vs Stocks
```{r}
Threept_vs_stocks <- player_3pt_summary_playoffs %>% 
 filter(TOTAL_FG3A >= 20)

Threept_vs_stocks_plot <- ggplot(Threept_vs_stocks, aes(x = STOCKS, y = SHOT_QUALITY_2)) +
  #geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_hline(yintercept = league_avg_3p_value * 100, linetype = "dashed", color = "red2") +
  geom_image(aes(image = IMG_URL), 
             size = 0.15, 
             asp = 1.0,
             position = position_jitter(width = 0.15, height = 0.5)) +
  labs(
    title = "2025 NBA Playoffs: 3PT% vs Stocks",
    subtitle = "Min. 20 3PA | Source: nba.com via hoopR",
    x = "Steals + Blocks (Stocks)", 
    y = "Shot Quality (3P%)"
  ) +
  theme_classic() +
    theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 18))
Threept_vs_stocks_plot

ggsave("Threept_vs_stocks_plot.png", width = 10, height = 8, dpi = 300)
```


#2025 NBA Playoffs: 3PT% vs Plus Minus
```{r}
#create new plot for plus minus and 3pt%

Threept_vs_plus_minus_plot <- player_3pt_summary_playoffs %>% 
 filter(TOTAL_FG3A >= 20)

Threept_vs_plus_minus_plot <- ggplot(Threept_vs_plus_minus_plot, aes(x = TOTAL_PLUS_MINUS, y = SHOT_QUALITY_2)) +
  #geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_hline(yintercept = league_avg_3p_value * 100, linetype = "dashed", color = "red2") +
  geom_image(aes(image = IMG_URL), 
             size = 0.15, 
             asp = 1.0,
             position = position_jitter(width = 0.15, height = 0.5)) +
  labs(
    title = "2025 NBA Playoffs: 3PT% vs Plus Minus",
    subtitle = "Min. 20 3PA | Source: nba.com via hoopR",
    x = "Total Individual Plus Minus", 
    y = "Shot Quality (3P%)"
  ) +
  theme_classic() +
    theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 18))
Threept_vs_plus_minus_plot

ggsave("C:/Users/cmlando/OneDrive - Emory/Desktop/R Files/NBA Visualization/Threept_vs_plus_minus_plot.png", width = 10, height = 8, dpi = 300)
```

## Data Cleaning for regular Season
```{r}
logs_rs <- nba_playergamelogs(
  season = "2024-25",
  season_type = "Regular Season",
  league_id = "00",  # NBA (not G-League etc.)
  player_id = NULL   # <- THIS is what ensures it's not limited to just LeBron
)

# Extract actual log data
player_games_rs <- logs_rs$PlayerGameLogs

# Check number of rows (should be 100s)
nrow(player_games_rs)


player_3pt_summary_Regular <- player_games_rs %>%
  select(PLAYER_NAME, PLAYER_ID, TEAM_ABBREVIATION, GAME_DATE,
         FG3M, FG3A, FG3_PCT, BLK, STL, PLUS_MINUS, REB, TOV, AST) %>%
  mutate(
    FG3M = as.numeric(FG3M),
    FG3A = as.numeric(FG3A),
    FG3_PCT = as.numeric(FG3_PCT),
    BLK = as.numeric(BLK),
    STL = as.numeric(STL),
    REB = as.numeric(REB),
    TOV = as.numeric(TOV),
    AST = as.numeric(AST),
    PLUS_MINUS = as.numeric(PLUS_MINUS)
  ) %>%
  group_by(PLAYER_NAME, PLAYER_ID) %>%
  summarise(
    TOTAL_FG3M = sum(FG3M, na.rm = TRUE),
    TOTAL_STLS = sum(STL, na.rm = TRUE),
    TOTAL_FG3A = sum(FG3A, na.rm = TRUE),
    AVG_FG3_PCT = mean(FG3_PCT, na.rm = TRUE),
    AVG_FG3_PCT2 = ifelse(TOTAL_FG3A == 0, 0, TOTAL_FG3M / TOTAL_FG3A),
    BPG = mean(BLK, na.rm = TRUE),
    SPG = mean(STL, na.rm = TRUE),
    RPG = mean(REB, na.rm = TRUE),
    TPG = mean(TOV, na.rm = TRUE),
    APG = mean(AST, na.rm = TRUE),
    STOCKS = sum(BPG, SPG, na.rm = TRUE),
    TOTAL_PLUS_MINUS = sum(PLUS_MINUS, na.rm = TRUE),
    GP = n(),
    .groups = "drop"
  ) 

##### left off here, need to fix 3pt average


player_3pt_summary_Regular <- player_3pt_summary_Regular %>%
  mutate(IMG_URL = paste0("https://cdn.nba.com/headshots/nba/latest/1040x760/", PLAYER_ID, ".png"))

player_3pt_summary_Regular_avg <- player_3pt_summary_Regular %>%  
   filter(TOTAL_FG3A >= 1)

league_avg_3p_rs <- mean(player_3pt_summary_Regular_avg$AVG_FG3_PCT2, na.rm = TRUE)

player_3pt_summary_Regular <- player_3pt_summary_Regular %>%
  mutate(
    SHOT_QUALITY = AVG_FG3_PCT*100,
    SHOT_QUALITY_2 = AVG_FG3_PCT2*100,
    SHOT_MAKING = AVG_FG3_PCT2*100 - league_avg_3p_rs*100
  )

league_avg_3p_rs <- player_3pt_summary_Regular %>%
  filter(TOTAL_FG3A >= 1) %>%
  summarise(
    league_avg = sum(TOTAL_FG3M, na.rm = TRUE) / sum(TOTAL_FG3A, na.rm = TRUE)
  ) 

league_avg_3p_value_rs <- pull(league_avg_3p_rs, league_avg)
```


# 2025 NBA Regular Season: 3PT% vs Stocks
```{r}
Threept_vs_stocks_plot <- player_3pt_summary_Regular %>% 
 filter(TOTAL_FG3A >= 200)

Threept_vs_stocks_plot <- ggplot(Threept_vs_stocks_plot, aes(x = STOCKS, y = SHOT_QUALITY_2)) +
  #geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_hline(yintercept = league_avg_3p_value_rs * 100, linetype = "dashed", color = "red2") +
  geom_image(aes(image = IMG_URL), 
             size = 0.15, 
             asp = 1.0,
             position = position_jitter(width = 0.15, height = 0.5)) +
  labs(
    title = "2025 NBA Regular Season: 3PT% vs Stocks",
    subtitle = "Min. 200 3PA | Source: nba.com via hoopR",
    x = "Steals + Blocks (Stocks)", 
    y = "Shot Quality (3P%)"
  ) +
  theme_classic() +
    theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 18))
Threept_vs_stocks_plot

ggsave("C:/Users/cmlando/OneDrive - Emory/Desktop/R Files/NBA Visualization/Threept_stocks_RS.png", width = 10, height = 8, dpi = 300)
```


# 2025 NBA Regualar Season: 3PT% vs Plus Minus
```{r}
Threept_vs_plus_minus_plot <- player_3pt_summary_Regular %>% 
 filter(TOTAL_FG3A >= 200)

Threept_vs_plus_minus_plot <- ggplot(Threept_vs_plus_minus_plot, aes(x = TOTAL_PLUS_MINUS, y = SHOT_QUALITY_2)) +
  #geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_hline(yintercept = league_avg_3p_value_rs * 100, linetype = "dashed", color = "red2") +
  geom_image(aes(image = IMG_URL), 
             size = 0.15, 
             asp = 1.0,
             position = position_jitter(width = 0.5, height = 0.75)) +
  labs(
    title = "2025 NBA Regualar Season: 3PT% vs Plus Minus",
    subtitle = "Min. 200 3PA | Source: nba.com via hoopR",
    x = "Total Individual Plus Minus", 
    y = "Shot Quality (3P%)"
  ) +
  theme_classic() +
    theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 18))
Threept_vs_plus_minus_plot

ggsave("C:/Users/cmlando/OneDrive - Emory/Desktop/R Files/NBA Visualization/Threept_vs_plus_minus_RS.png", width = 10, height = 8, dpi = 300)
```


# 2025 NBA Regualar Season: Rebounds vs Blocked Shots
```{r}
Rebounds_blocks <- player_3pt_summary_Regular %>% 
  filter(RPG >= 6.0)

Rebounds_blocks <- ggplot(Rebounds_blocks, aes(x = RPG, y = BPG)) +
  geom_image(aes(image = IMG_URL), 
             size = 0.15, 
             asp = 1.0,
             position = position_jitter(width = 0.5, height = 0.5)) +
  labs(
    title = "2025 NBA Regualar Season: Rebounds vs Blocked Shots",
    subtitle = "Min. 6 RPG | Source: nba.com via hoopR",
    x = "Rebounds Per Game", 
    y = "Blocks Per Game"
  ) +
  theme_classic() +
    theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 18))
Rebounds_blocks

ggsave("C:/Users/cmlando/OneDrive - Emory/Desktop/R Files/NBA Visualization/Rebounds_blocks_RS.jpg", width = 10, height = 8, dpi = 300)

```


# 2025 NBA Playoffs: Rebounds vs Blocked Shots
```{r}
Rebounds_blocks_po <- player_3pt_summary_playoffs %>% 
  filter(RPG >= 5.0)

Rebounds_blocks_po <- ggplot(Rebounds_blocks_po, aes(x = RPG, y = BPG)) +
  geom_image(aes(image = IMG_URL), 
             size = 0.15, 
             asp = 1.0,
             position = position_jitter(width = 0.5, height = 0.5)) +
  labs(
    title = "2025 NBA Playoffs: Rebounds vs Blocked Shots",
    subtitle = "Min. 5 RPG | Source: nba.com via hoopR",
    x = "Rebounds Per Game", 
    y = "Blocks Per Game"
  ) +
  theme_classic() +
    theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 18))
Rebounds_blocks_po

ggsave("C:/Users/cmlando/OneDrive - Emory/Desktop/R Files/NBA Visualization/Rebounds_blocks_Playoffs.jpg", width = 10, height = 8, dpi = 300)

```
# NBA regular Season: Blocks vs Rebounds among 3pt shooters
```{r}

Rebounds_blocks_stretch <- player_3pt_summary_Regular %>% 
filter(TOTAL_FG3M >= 50 & RPG >= 5.0) 

Rebounds_blocks_stretch <- ggplot(Rebounds_blocks_stretch, aes(x = RPG, y = BPG)) +
  geom_image(aes(image = IMG_URL), 
             size = 0.15, 
             asp = 1.0,
             position = position_jitter(width = 0.5, height = 0.5)) +
  labs(
    title = "2025 NBA Regualar Season: Rebounds vs Blocked Shots",
    subtitle = "Min. 50 3pt FG Made and 5 RPG  | Source: nba.com via hoopR",
    x = "Rebounds Per Game", 
    y = "Blocks Per Game"
  ) +
  theme_classic() +
    theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 18))
Rebounds_blocks_stretch

ggsave("C:/Users/cmlando/OneDrive - Emory/Desktop/R Files/NBA Visualization/Rebounds_blocks_stretch_RS.jpg", width = 10, height = 8, dpi = 300)

```

#Per 36
```{r}
Per36  <- player_games_rs %>%
  select(PLAYER_NAME, PLAYER_ID, TEAM_ABBREVIATION, GAME_DATE,
         FG3M, FG3A, FG3_PCT, BLK, STL, PLUS_MINUS, REB, MIN) %>%
  mutate(
    FG3M = as.numeric(FG3M),
    FG3A = as.numeric(FG3A),
    FG3_PCT = as.numeric(FG3_PCT),
    BLK = as.numeric(BLK),
    STL = as.numeric(STL),
    REB = as.numeric(REB),
    MIN = as.numeric(MIN),
    PLUS_MINUS = as.numeric(PLUS_MINUS)
  ) %>%
  group_by(PLAYER_NAME, PLAYER_ID) %>%
  summarise(
    TOTAL_FG3M = sum(FG3M, na.rm = TRUE),
    TOTAL_FG3A = sum(FG3A, na.rm = TRUE),
    AVG_FG3_PCT = mean(FG3_PCT, na.rm = TRUE),
    BPG = sum(BLK, na.rm = TRUE),
    SPG = sum(STL, na.rm = TRUE),
    RPG = sum(REB, na.rm = TRUE),
    TOTAL_PLUS_MINUS = sum(PLUS_MINUS, na.rm = TRUE),
    TOTAL_MIN = sum(MIN, na.rm = TRUE),
    GP = n(),
    .groups = "drop"
  ) %>%
  mutate(
    STOCKS = BPG + SPG,
    STOCKS_PER36 = (STOCKS / TOTAL_MIN) * 36,
    FG3M_PER36 = (TOTAL_FG3M / TOTAL_MIN) * 36,
    REB_PER36 = (RPG / TOTAL_MIN) * 36,
    BLK_PER36 = (BPG / TOTAL_MIN) * 36,
    PLUS_MINUS_PER36 = (TOTAL_PLUS_MINUS / TOTAL_MIN) * 36
  ) 

Per36 <- Per36 %>%
  mutate(IMG_URL = paste0("https://cdn.nba.com/headshots/nba/latest/1040x760/", PLAYER_ID, ".png"))

Rebounds_blocks_36 <- Per36 %>% 
  filter(REB_PER36 >= 9.0 & GP >= 10)  # Threshold

Rebounds_blocks_36 <- ggplot(Rebounds_blocks_36, aes(x = REB_PER36, y = BLK_PER36)) +
  geom_image(aes(image = IMG_URL), 
             size = 0.15, 
             asp = 1.0,
             position = position_jitter(width = 0.5, height = 0.5)) +
  labs(
    title = "2025 NBA Regualar Season: Rebounds vs Blocks (Per 36 mins)",
    subtitle = "Min. 9 RPG/36 and 10 GP | Source: nba.com via hoopR",
    x = "Rebounds Per Game", 
    y = "Blocks Per Game"
  ) +
  theme_classic() +
    theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 18))
Rebounds_blocks_36

ggsave("C:/Users/cmlando/OneDrive - Emory/Desktop/R Files/NBA Visualization/Rebounds_blocks_RS_36.jpg", width = 10, height = 8, dpi = 300)


#### For stretch Bigs

Rebounds_blocks_36_stgretch <- Per36 %>% 
  filter(REB_PER36 >= 9.0 & TOTAL_FG3A >= 50)  # Threshold

Rebounds_blocks_36_stgretch <- ggplot(Rebounds_blocks_36_stgretch, aes(x = REB_PER36, y = BLK_PER36)) +
  geom_image(aes(image = IMG_URL), 
             size = 0.15, 
             asp = 1.0,
             position = position_jitter(width = 0.5, height = 0.5)) +
  labs(
    title = "2025 NBA Regualar Season: Rebounds vs Blocks (Per 36 mins)",
    subtitle = "Min. 9 RPG/36 and Min 50 3PTA | Source: nba.com via hoopR",
    x = "Rebounds Per Game", 
    y = "Blocks Per Game"
  ) +
  theme_classic() +
    theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 18))
Rebounds_blocks_36_stgretch

ggsave("C:/Users/cmlando/OneDrive - Emory/Desktop/R Files/NBA Visualization/Rebounds_blocks_stretch_RS_36.jpg", width = 10, height = 8, dpi = 300)
```
#2025 NBA Regualar Season: Assists vs Turnovers
```{r}

TOs_Assits <- player_3pt_summary_Regular %>% 
    filter(TOTAL_STLS >= 50) 
  
TOs_Assits <- ggplot(TOs_Assits, aes(x = TPG, y= APG)) +
  geom_image(aes(image = IMG_URL), 
             size = 0.15, 
             asp = 1.0,
             position = position_jitter(width = 0.5, height = 0.5)) +
  labs(
    title = "2025 NBA Regualar Season: Assists vs Turnovers",
    subtitle = "Min. 82 Steals  | Source: nba.com via hoopR",
    x = "Turnovers Per Game", 
    y = "Assists Per Game"
  ) +
  theme_classic() +
    theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 18))
TOs_Assits

ggsave("C:/Users/cmlando/OneDrive - Emory/Desktop/R Files/NBA Visualization/assists_TOs.jpg", width = 10, height = 8, dpi = 300)
```



#2025 NBA Regualar Season: Assists vs Steals
```{r}
STLs_Assits <-  player_3pt_summary_Regular %>% 
  filter(TOTAL_STLS >= 50)  # Minimum attempts threshold


STLs_Assits <- ggplot(STLs_Assits, aes(x = SPG, y= APG)) +
  geom_image(aes(image = IMG_URL), 
             size = 0.15, 
             asp = 1.0,
             position = position_jitter(width = 0.5, height = 0.5)) +
  labs(
    title = "2025 NBA Regualar Season: Assists vs Steals",
    subtitle = "Min. 82 Steals  | Source: nba.com via hoopR",
    x = "Steals Per Game", 
    y = "Assists Per Game"
  ) +
  theme_classic() +
    theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 18))
STLs_Assits

ggsave("C:/Users/cmlando/OneDrive - Emory/Desktop/R Files/NBA Visualization/assists_STLs.jpg", width = 10, height = 8, dpi = 300)
```
# Build catch all metric using Math and Sport's formula
```{r}
# Make catch all metric

# Step 1: Create TEAM_WINS table
team_wins_2025 <- player_games_rs %>%
  select(TEAM_ABBREVIATION, GAME_DATE, WL) %>%
  distinct(TEAM_ABBREVIATION, GAME_DATE, .keep_all = TRUE) %>%  # One row per team-game
  mutate(WIN = ifelse(WL == "W", 1, 0)) %>%
  group_by(TEAM_ABBREVIATION) %>%
  summarise(WINS = sum(WIN, na.rm = TRUE), .groups = "drop")

# Step 2: Find each player's primary team (most games played)
player_primary_team <- player_games_rs %>%
  count(PLAYER_ID, TEAM_ABBREVIATION, name = "GAMES_PLAYED") %>%
  group_by(PLAYER_ID) %>%
  slice_max(GAMES_PLAYED, n = 1, with_ties = FALSE) %>%
  ungroup()


# Step 3: Calculate player-level metric and attach team
player_custom_metric_2025 <- player_games_rs %>%
  select(
    PLAYER_NAME, PLAYER_ID, TEAM_ABBREVIATION, GAME_DATE,
    PTS, FGA, FTA, MIN, FG3A, FG3M,
    STL, BLK, AST, TOV, REB, PLUS_MINUS
  ) %>%
  mutate(
    MIN = as.numeric(MIN),
    across(c(PTS, FGA, FTA, FG3A, FG3M, STL, BLK, AST, TOV, REB, PLUS_MINUS), as.numeric)
  ) %>%
  filter(!is.na(MIN)) %>%
  group_by(PLAYER_ID, PLAYER_NAME) %>%
  summarise(
    GP = n(),
    AVG_PTS = mean(PTS, na.rm = TRUE),
    AVG_FGA = mean(FGA, na.rm = TRUE),
    AVG_FTA = mean(FTA, na.rm = TRUE),
    AVG_MIN = mean(MIN, na.rm = TRUE),
    AVG_FG3A = mean(FG3A, na.rm = TRUE),
    AVG_STL = mean(STL, na.rm = TRUE),
    AVG_BLK = mean(BLK, na.rm = TRUE),
    AVG_AST = mean(AST, na.rm = TRUE),
    AVG_TOV = mean(TOV, na.rm = TRUE),
    AVG_REB = mean(REB, na.rm = TRUE),
    AVG_PM  = mean(PLUS_MINUS, na.rm = TRUE),
    CUSTOM_METRIC = 
      AVG_PTS * 1.2 -
      AVG_FGA * 0.96 -
      AVG_FTA * 0.39 +
      AVG_MIN * 0.09 +
      AVG_FG3A +
      AVG_STL * 1.2 +
      AVG_BLK * 1.5 +
      AVG_AST * 0.6 -
      AVG_TOV +
      AVG_REB * 0.3 +
      AVG_PM * 0.34,
    .groups = "drop"
  ) %>%
  filter(GP >= 10) %>%
  left_join(player_primary_team, by = "PLAYER_ID") %>%
  left_join(team_wins_2025, by = "TEAM_ABBREVIATION") %>%
  arrange(desc(CUSTOM_METRIC))



# Visualize the data
top10 <- player_custom_metric_2025 %>%
  slice_max(CUSTOM_METRIC, n = 30)

# Then plot using ggplot2 in R
library(ggplot2)

ggplot(top10, aes(x = reorder(PLAYER_NAME, CUSTOM_METRIC), y = CUSTOM_METRIC)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Top 30 NBA Players by Catch-all Metric Prototype (2025)",
    x = "Player",
    y = "Custom Metric Score"
  ) +
  theme_minimal() +
  theme_classic() +
    theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 18))
ggsave("C:/Users/cmlando/OneDrive - Emory/Desktop/R Files/NBA Visualization/custom_metric_top30.jpg", width = 10, height = 8, dpi = 300)


player_index <- hoopR::nba_playerindex()$PlayerIndex

names(player_index)

player_meta_clean <- player_index %>%
  select(PERSON_ID, DISPLAY_FIRST_LAST = PLAYER_FIRST_NAME, POSITION, TEAM_ABBREVIATION) %>%
  mutate(DISPLAY_FIRST_LAST = as.character(DISPLAY_FIRST_LAST))  # match merge type


player_custom_metric_2025_pos <- player_custom_metric_2025 %>%
  left_join(player_meta_clean, by = c("PLAYER_ID" = "PERSON_ID"))
```


```{r}
# Ended here 06/17/25
# Next steps: 
#   - figure out best way to collapse multiple player positions (F-C), etc. 
#   - Get updated regression coefficients for catch all
#   - Exxplore data by position

```

